### 2016-08-26 section/6_related.tex
address linhai comments
finish threats to validity

Recently proposed tools go beyond profiling and provide more automated analysis.
They can identify slow call-stack patterns inside event handlers
\cite{Han:2012:PDL:2337223.2337241}, help understand performance causality
relationship among system components
\citet{TaoAsplos2014}, identify inputs 
or configuration entries that are most responsible for performance problems
\cite{Attariyan:2012:XAR:2387880.2387910},
and estimate the performance impact of any
potential optimization at any point of a multi-threaded program
\cite{coz.sosp15}. 
They all target different problems from \Tool. 
\comment{
\Tool targets 
inefficient loops, a common
inefficiency problem that contributes to
about two thirds of real-world user-perceived performance problems studied
by previous work \cite{SongOOPSLA2014}, and tries to pin-point the exact
root cause and provide fix-strategy suggestions.
}

>>>>

Recently proposed tools go beyond profiling.
They can identify slow call-stack patterns inside event handlers
\cite{Han:2012:PDL:2337223.2337241}, help understand performance causality
relationship among system components
\cite{TaoAsplos2014}, identify inputs 
or configuration entries that are most responsible for performance problems
\cite{Attariyan:2012:XAR:2387880.2387910},
and estimate the performance impact of any
potential optimization at any point of a multi-threaded program
\cite{coz.sosp15}. 
They all target different problems from \Tool. 
\comment{
\Tool targets 
inefficient loops, a common
inefficiency problem that contributes to
about two thirds of real-world user-perceived performance problems studied
by previous work \cite{SongOOPSLA2014}, and tries to pin-point the exact
root cause and provide fix-strategy suggestions.
}

### 2016-08-26 section/threats.tex
finish threats to validity

Of course, our taxonomy does not cover \emph{all} loop inefficiency problems.
For example, some loops may be vulnerable to false sharing problems or lock
contention problems, which are out of the scope of our taxonomy.

The static program analysis and optimization.
This analysis is complete, but not sound. We may identify side-effect
instructions that are actually not (Section \ref{sec:s_workless}).
The optimization discussed in Section \ref{sec:perf}.

The resuleless and redundancy rate thresholds could lead to false positives
and false negatives.

Our evaluation.
What presented above reflects our best effort in assessing our root-cause
taxonomy using a non-biased set of real-world inefficient loop problems that
have been perceived by users and fixed by developers.

The numbers presented above should be interpreted together with our methodology
and should not be overly generalized.
The performance bugs examined above cover a variety of applications, workload, 
development environments and programming languages. 
However, there are definitely uncovered cases, like problems in distributed systems
and scientific computing systems, and others.

Previous work~\cite{PerfBug, SongOOPSLA2014} uses developers tagging and
on-line discussion to judge whether a bug report is about
performance problems and whether 
the performance problem under discussion is noticed and reported by users
or not.
We do not intentionally ignore any aspect of loop-related performance problems. 
Some loop-related performance problems may never be noticed by end users
or never be fixed by developers, and hence skip our study. However,
there are no conceivable ways to study them.

>>>>

\Tool does not cover all loop inefficiency problems.
For example, it does not handle performance problems caused by
cache-line false sharing in multi-core machines or lock
contention issues. It also cannot provide useful fixing 
suggestions for 1* inefficient loops, as discussed in 
Section \ref{sec:coverage}.

The static analysis in \Tool could occasionally lead to inaccurate diagnosis.
Specifically, \Tool static analysis could conservatively identify some
non-side-effect instructions, such as a write to a heap variable that
is not used after the loop, as having side effects 
(Section \ref{sec:s_workless}). 
The SE-based optimization discussed in Section \ref{sec:perf} could cause
false positives in cross-loop redundancy diagnosis.
These cases are all rare in practice and not encountered in our experiments.

Our default settings of resultless and redundancy rate thresholds 
work well in our evaluation. However, they could potentially lead to false 
positives and false negatives, as discussed in Section \ref{sec:sensi}.

The results presented in Section \ref{sec:eval_taxonomy}
and Section \ref{sec:experiment}
should be interpreted together with corresponding methodologies
and not be overly generalized.
They reflect our best effort in evaluating our root-cause
taxonomy and \Tool using a non-biased set of real-world inefficient loop 
problems that have been perceived by users and fixed by developers.
The benchmark suite covers a variety of applications, workload, 
development environments and programming languages. 
However, there are definitely uncovered cases, like problems in distributed systems
and scientific computing systems, and others. 
Furthermore, although
we did not intentionally ignore any aspect of loop-related performance problems,
some loop-related problems may never be noticed by end users
or never be fixed by developers, and hence may skip our evaluation. However,
there are no conceivable ways to study them, particularly considering that 
\Tool is designed to diagnose already-manifested performance problems not to
predict not-yet-observed problems.
